### 2023-08-25 Notes/annote_bib.tex
Prepared report for Dr. Fuller about linear estimator being better than proposed estimator.

>>>>

% \subsection*{Chen and Kim (2014)}
% \begin{description}
%   \item[Title:] Population Empirical Likelihodd for Nonparametric Inference in
%     Survey Sampling
%   \item[Author:] Sixia Chen and Jae Kwang Kim
%   \item[Journal (Year):] Statistica Sinica (2014)
%   \item[Summary:]
%   \item[Limitations:]\;
%     \begin{itemize}
%       \item
%     \end{itemize}
%   \item[Extensions:]\;
%     \begin{itemize}
%       \item
%     \end{itemize}
% \end{description}

\subsection*{Chen et al. (2022)}
\begin{description}
  \item[Title:] Nonparametric Mass Imputation for Data Integration
  \item[Author:] Sixia Chen, Shu Yang, Jae Kwang Kim
  \item[Journal (Year):] JSSM (2022)
  \item[Summary:] This paper aims to combine data from a probability sample
    $A$ and a non-probability sample $B$ using non-parametric methods. We 
    assume the $X$ is observed in $A$ and $B$ but $Y$ is only available in $B$. 
    It achieves this goal by using a kernel estimator for the outcome model
    $m(x)$ on sample $B$ and then using this model to predict missing values of
    $Y$ for $A$. Since the sample weights in $A$ are valid, these are used to 
    adjust the predicted values $\hat m(x)$. Variance estimates are also given.
  \item[Limitations:]\;
    \begin{itemize}
      \item The model require MAR for the response model in $B$.
    \end{itemize}
  \item[Extensions:]\;
    \begin{itemize}
      \item Can we extend this to multiple non-probability samples?
    \end{itemize}
\end{description}

\subsection*{Hidiroglou (2001)}
\begin{description}
  \item[Title:] Double Sampling
  \item[Author:] M. A. Hidiroglou
  \item[Journal (Year):] Survey Methodology (2001)
  \item[Summary:] This paper produces the optimal regression estimator for 
    non-nested probability samples. This occurs when sample $A$ observes $X$ 
    while $B$ observes $X$ and $Y$ but unlike two-phase sampling there is no
    overlap between the observed values for $X$ in $A$ and $B$.

    This paper also explores the connection between non-nested samples and 
    calibration.
  \item[Limitations:]\;
    \begin{itemize}
      \item Unclear to me which class of estimators we are optimizing within.
    \end{itemize}
  \item[Extensions:]\;
    \begin{itemize}
      \item How to extend to a third category?
    \end{itemize}
\end{description}

\subsection*{Park and Kim (2019)}
\begin{description}
  \item[Title:] Mass Imputation for Two-Phase Sampling
  \item[Author:] Seho Park and Jae Kwang Kim
  \item[Journal (Year):] arXiv (2019)
  \item[Summary:] This paper proposes a mass imputation estimator for 
    estimating the total from a two-phase sample. Instead of using an
    estimate from phase 1 data and combining it with phase 2 data, this
    approach uses a regression model to predict the missing data in phase 
    1. The paper shows how this result is consistent with previous 
    estimates and they provide a variance estimator.
  \item[Limitations:]\;
    \begin{itemize}
      \item What if the regression model is incorrect?
      \item Does this account for enough uncertainty if just the predicted
        values are used?
    \end{itemize}
  \item[Extensions:]\;
    \begin{itemize}
      \item How can this be extended to another phase.
    \end{itemize}
\end{description}
